How Does Certain Chemical Attributes Influence Wine Quality? by Daniel Jin
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}

library(ggplot2)
library(dplyr)
library(readr)
library(reshape2)
library(beeswarm)
library(GGally)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
setwd("C:/Users/Skywind/Desktop/Backup2/R/Udacity")
df <- read_csv('wineQualityReds.csv', col_names = FALSE)
df <- subset(df, select = -X1)
names(df) <- df[1,]
df <- df[2:nrow(df),]
df[,] <- sapply(df[, c(1:length(df))], as.numeric)
```



>This tidy dataset contains 1599 rows of data representing 1599 different
Portugeuse "Vinho Verde" red wines. One of the variables is "quality" which
is rated between 0 and 10. The number on each wine is rated by at least 3
wine experts. The other 11 variables are chemical attributes of the wine.
More information can be found at: 
https://s3.amazonaws.com/udacity-hosted-downloads/ud651/wineQualityInfo.txt

>I am to find how each chemical attribute influence the quality of red wines.


# Univariate Plots Section

```{r echo=FALSE, warning = FALSE, Univariate_Plots}
glimpse(df)
```

Here we see that all of our variables are continuous variables. Quality should
be an ordinal categorical variable, but will not change it since it is more
convenient for analysis to leave as a continuous variable.


```{r, echo = FALSE}
summary(df)
```

We see that some of these variables have at least one outlier given that the
max is significantly higher than the Q3. The exact method is to find points the
points 1.5IQR less than the Q1 or 1.5IQR more than the Q3. Since we don't
really care about exacts, we won't do this.


```{r echo = FALSE}
df_no_quality <- subset(df, select = -quality)

ggplot(data = melt(df_no_quality), mapping = aes(x = value)) +
  geom_histogram(bins = 10) +
  facet_wrap(~variable, scales = 'free_x')

```

Above we see that 'density', 'volatile.acidity' and 'pH' have relatively normal 
distributions. 'residual.sugar' and 'chlorides' has a heavy right tail. These columns 
require a transformation or swarmplot to visualize better. 'fixed.acidity', 
'free.sulfur.dioxide', 'total.sulfur.dioxide', 'sulphates', and 'alcohol'
are right skewed. 'citric acid' has nearly a uniform distribution but is a bit
right skewed.

```{r}
ggplot(data = df, aes(x = quality)) +
  geom_bar()
```

Most wine experts rated wines a 5 or 6. More rated above 6 than below 5.


```{r echo = FALSE}

for (variable in c('residual.sugar', 'chlorides')) {
  
  beeswarm(df[,variable], vertical = TRUE, cex = 0.5,
           main = paste('Swarm Plot of ', names(df[,variable])))
}

```

Above we see a better view on the distribution of the residual.sugar variable
and the chlorides variable compared to the histograms.For residual.sugar,
the bulk of the data is around 2-3. There are multiple points above the 7.5+
threshhold so it's clear that it's not just a few outliers.

We see something similar to chlorides. The bulk of the data is around 0.1. 
There are more than a few outliers in the 0.2+ threshhold. 

Compared to the histograms we can visualize the number of outliers more clearly.

# Univariate Analysis

### What is the structure of your dataset?

There are 1599 observations with 12 variables. All the variables are
numeric variables.Although the 'quality' variable is technically an integer
variable since there are no decimals associated with rating, it is left
coded as a numeric variable.

The average quality rating is 5.636, the median is 6, and the mode is 5. This
shows that quality is a bit right skewed because the median > mean.

### What is/are the main feature(s) of interest in your dataset?

Since I don't know anything about red wine or the attributes about good or
bad wine, it is hard to say.

I would assume that anything to do with taste would have an effect on
quality. By reading the variable dictionary in the link provided, this includes:
volatile acidity, citric acid, residual sugar, chlorides, total sulfur
dioxide, and alcohol.

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

I think all the variables in the dataset are of interest since I have no
domain knowledge. So the remaining variables not previously mentioned will
need to be investigated. This includes: fixed acidity, free sulfur dioxide,
density, pH, and sulphates.


### Did you create any new variables from existing variables in the dataset?

I did not create any new variables from existing variables.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

I did not transform any of the variables. I was able to visualize them using
histograms and swarmplots. citric.acid had an unusual uniform-like
distribution. 


# Bivariate Plots Section

```{r echo=FALSE, fig.width = 8, fig.height = 8}
ggcorr(data = df,
       method = c('all.obs', 'spearman'),
       nbreaks = 4,
       label = TRUE,
       name = 'Spearman Correlation',
       hjust = 0.8,
       size = 3,
       angle = -50) +
  ggtitle('Spearman Correlation Matrix')
```

We see a negative correlation between volatile.acid with quality and a weak 
positive correlation between citric.acid and quality. There is a moderate 
correlation between alcohol and quality and sulphates and quality. Note that
this means that as alcohol percent increases, quality tends to increase. The
spearman correlation coefficient measures monotonic relationships instead of
linear with pearson's correlation coefficient.

```{r echo=FALSE, fig.width = 8, fig.height = 8}
ggcorr(data = subset(df, select = -quality), 
       label = TRUE,
       name = 'Pearson Correlation',
       nbreaks = 4,
       hjust = 0.8, 
       size = 3, 
       angle = -50) +
  ggtitle('Pearson Correlation Matrix')

```

Some of the correlations we see above is as expected. There is a moderate
negative correlation between citric.acid and pH. This means that as citric.acid
increases, the pH goes down. This makes sense because a lower pH means that the
solution is more acidic.We observe a moderate-strong negative correlation
between fixed.acidity and pH. There is a strange weak positive correlation
between volatile acidity and pH. This is most likely due to having a higher pH
compared to fixed.acidity and citric.acid. There is a strong positive 
correlation between fixed.acidity and citric.acid with a weak negative
correlation between  fixed.acidity and volatile.acidity. 

In general, these three acidic variables
are a bit correlated with two of them being weakly or moderate-weakly
correlated with quality. It may be more sightful to examine them further.

```{r echo=FALSE}
ggplot(aes(x = fixed.acidity, y = citric.acid), data = df) +
  geom_point(alpha = 1/5)

ggplot(aes(x = volatile.acidity, y = citric.acid), data = df) +
  geom_point(alpha = 1/5)

ggplot(aes(x = fixed.acidity, y = volatile.acidity), data = df) +
  geom_point(alpha = 1/5)

```

We see the relationship between these 3 acids more clearly above. When
fixed.acidity increases, volatile.acidity decreases while citric.acid increases.
When volatile.acidity increases, citric.acid tends to decrease. This lines up
with the previous observation because it is the same thing as saying that when
fixed.acidity decreases, volatile.acidity increases while citric.acid
decreases because fixed.acidity decreases.

Due to a lack of domain knowledge, it is not clear if this is by coincidence
or that when one decreases, the other one naturally increases. 

It does make sense that when volatile.acidity increases, quality goes down
because the taste of vinegar is stronger.

> Since quality is divided into 3,4,5,6,7,8 with the mode/median at 5/6, it
could be useful to create a new variable for know if a wine is low quality,
medium quality, or high quality based on these values. This could lead to more
interesting visualizations when this new variable is an ordered factor.

```{r }
df$quality.type <- ifelse(df$quality > 6, 'High', ifelse(df$quality > 4,
                                                         'Medium', 'Low'))
df$quality.type <- factor(df$quality.type, levels = c('Low', 'Medium', 'High'))
```

```{r , echo = FALSE, Boxplot_function}
Make_boxplot <- function(var_x, var_y) {

  ggplot(aes_q(x = substitute(var_x), y = substitute(var_y)), data = df) +
    geom_boxplot()
  
}

```


```{r echo=FALSE}
Make_boxplot(quality.type, volatile.acidity)

by(df$volatile.acidity, df$quality.type, summary)
```

The above plot clearly shows that higher quality wines tend to have less 
volatile acidity in them.

```{r echo=FALSE}
Make_boxplot(quality.type, fixed.acidity)

by(df$fixed.acidity, df$quality.type, summary)
```

On average, higher quality wines tend to have a higher fixed acidity.

```{r echo=FALSE}
Make_boxplot(quality.type, citric.acid)

by(df$citric.acid, df$quality.type, summary)
```

On average, high quality wines tend to have higher citric acid content.

```{r echo=FALSE}
Make_boxplot(quality.type, density)

by(df$density, df$quality.type, summary)
```

On average, higher quality wines have lower densities. The difference is
minimal.


```{r echo=FALSE}
Make_boxplot(quality.type, pH)

by(df$pH, df$quality.type, summary)
```

On average, low quality wines tend to have a higher pH

```{r echo=FALSE}
Make_boxplot(quality.type, sulphates)

by(df$sulphates, df$quality.type, summary)
```

On average, high quality wines tend to have higher sulphates

```{r echo=FALSE}
Make_boxplot(quality.type, alcohol)

by(df$alcohol, df$quality.type, summary)
```

On average, high quality wines tend to have higher alcohol content. There is no
difference between low and medium quality wines with varying alcohol content.
Most low and medium quality wines have between 9.5 to 11 percent alcohol
content. While high quality wines are around 11 to 12 percent.






```{r echo = FALSE}
summary_mean <- geom_line(stat = 'summary', fun.y = mean) 
summary_10q <- geom_line(stat = 'summary', fun.y = quantile, 
              fun.args = list(probs = .1), linetype = 3, color = 'blue') 
summary_90q <- geom_line(stat = 'summary', fun.y = quantile, 
              fun.args = list(probs = .9), linetype = 3, color = 'blue') 
summary_median <- geom_line(stat = 'summary', fun.y = quantile, 
                  fun.args = list(probs = .5),  color = 'blue')

ggplot(aes(x = round(residual.sugar/0.5)*0.5, y = quality), data = df) +
  geom_point(alpha = 1/5, size = 3 ,color = 'orange') +
  summary_mean + summary_10q + summary_90q + summary_median +
  scale_x_continuous(breaks = 1:16)

by(df$residual.sugar, df$quality.type, summary)
```

Residual sugar has no correlation with quality overall, but it appears that
quality peaks at around 6 and 8.5 using median as the measure. It peaks at
8.5 using mean as the measure. Given that the third quartile of residual
sugar is at 2.6, the peaks observed at likely due to a lack of wines past 5 for
residual sugar.

High quality wines have the highest median and mean residual sugar.

```{r  echo = FALSE}
ggplot(aes(x = round(chlorides/0.05)*0.05, y = quality), data = df) +
  geom_point(alpha = 1/5, size = 3 ,color = 'orange') +
  summary_mean + summary_10q + summary_90q + summary_median +
  scale_x_continuous(breaks = seq(0,0.7,0.10) )

by(df$chlorides, df$quality.type, summary)

```

Wine quality is highest when chlorides are minimized. Wine quality decreases
when chlorides increases toward the 0.10 value. But quality increases when
chlorides are between 0.2 and 0.25 and are equivalent to when chlorides are
about 0.05. After the chloride content in a wine increases past 0.25, the
quality only decreases. On average, wine quality decreases when there are
more chlorides in the wine.

High quality wines have the lowest median and average chloride content.

```{r echo = FALSE}
ggplot(aes(x = round(free.sulfur.dioxide/2.5)*2.5, y = quality), data = df) +
  geom_point(alpha = 1/5, size = 3 ,color = 'orange') +
  summary_mean + summary_10q + summary_90q + summary_median +
  scale_x_continuous(breaks = seq(0, 80, 10))

by(df$free.sulfur.dioxide, df$quality.type, summary)
```

There doesn't seem to be any significant relationship or trends of
free sulfur dioxide content in the wine with quality. However, on average
wines with free sulfur dioxide content of 55 tend to have a tiny bit higher
quality on average compared to other values of free sulfur dioxide.

Low quality wines have the lowest amount of median and mean free sulfur
dioxide.

```{r echo = FALSE}
ggplot(aes(x = round(total.sulfur.dioxide/10)*10, y = quality), data = df) +
  geom_point(alpha = 1/5, size = 3 ,color = 'orange') +
  summary_mean + summary_10q + summary_90q + summary_median +
  scale_x_continuous(breaks = seq(0, 300, 20))

by(df$total.sulfur.dioxide, df$quality.type, summary)
```

Wine quality increases drastically when total sulfur dioxide content is at
280-290, though this could just be outliers. Wine quality at 160 total sulfur 
dioxide is about the same as when there is around 10-40 total sulfur dioxide in 
the wine. The wines with between 40-160 total sulfur dioxide have the lowest
quality with the lowest at 120. Using median as the measure, wines appear to
have higher quality when total sulfur dioxide is around 60 or below.

Looking at the summary it looks like when there's too little total sulfur
dioxide it's associated with low quality wines.

>Since there could be a relationship between free sulfur dioxide and total
sulfur dioxide, I'll make a ratio between them to see if there's an ideal 
ratio

```{r}
df$free.total.sulfur <- df$free.sulfur.dioxide/df$total.sulfur.dioxide
```

```{r echo = FALSE}
ggplot(aes(x = free.total.sulfur, y = quality), data = df) +
  geom_point(alpha = 1/5) +
  geom_smooth(method = lm) +
  scale_x_continuous(breaks = seq(0,1,0.10))
```

It appears that as the ratio between free total sulfur dioxide to total sulfur
dioxide increases, the quality increases. The best ratio observed is around
0.85. 

# Bivariate Analysis


### Talk about some of the relationships you observed

Higher quality wines tend to have higher fixed acidity, lower volatile
acidity, higher citric acid, lower density, higher pH, higher sulphate,
and higher alcohol content when compared to medium and low quality wines.

Higher fixed acidity is associated with higher citric acid content, higher
volatile acid content is associated with lower citric acid content, and 
higher fixed acidity content is associated with lower volatile acid content.

The quality in a wine peaks when the residual sugar is around 6 or between
8.5 and 10.5. Higher quality wines have less chlorides in general. Wines with
a free sulfur dioxide content of around 55 have slightly higher qualities.
The highest quality wines have a total sulfur dioxide content of 280-290 using
median as the measure, though this is likely due to outliers. In general, a
total sulfur dioxide of around 60 and below are ideal. As the ratio between
free sulfur dioxide to total sulfur dioxide increases, the quality of wine
increases, with the best observed ratio at around 0.85.

With the summaries, we saw that higher quality wines have more residual sugar,
low quality wines have the least amount of free sulfur dioxide and total sulfur
dioxide.


### What was the strongest relationship you found?

Alcohol had the highest correlation for quality with a value of 0.5. The box
plot showing alcohol and quality was the only box plot with the first quartile
of the high quality group being around the same value of the 3rd quartile of
the other two groups. This clearly shows that higher quality wines tend to
have alcohol contents between 11 and 12 percent while low and medium quality
wines are between 9.5 and 11.

There is also a strong relationship between low volatile acidity and high
quality wine.


# Multivariate Plots Section

Earlier we saw that quality increases as the ratio of free sulfur dioxide to
total sulfur dioxide increases. We can see if the total sulfur dioxide in
the wine also plays a role in quality or does only the ratio matter.

```{r echo = FALSE}
ggplot(aes(x = free.total.sulfur, y = round(total.sulfur.dioxide/10)*10), 
       data = df) +
  geom_point(aes(color = quality.type)) +
  geom_smooth(aes(color = quality.type), method = lm) +
  coord_cartesian(ylim=c(0,80)) +
  scale_x_continuous(breaks = seq(0,1,0.10)) +
  scale_y_continuous(breaks = seq(0,300,10)) 

```

From the plot above it's interesting to see that there are two almost parallel
lines between the low quality and medium quality wine. The high quality
line is nearly between the two lines, but does overlap with the low quality
wines a little. 

In bivariate analysis, we thought that having a higher ratio between free
sulfur dioxide to total sulfur dioxide was better, but this is not the case.

In general, it seems that having a total sulfur dioxide
of around 15 to 50 and free to total sulfur dioxide ratio between 0.15 to
0.75 results in highest quality wine. One thing to keep in mind is that these
two depend on each other. In general, as the ratio between free and total
sulfur dioxide increases, the total sulfur dioxide should decrease.

We found previously that higher quality wines is associated with higher
residual sugar and more alcohol content. I know from common knowledge that low
alcohol percent are the ones that tend to have high residual sugar. We can 
adjust for the effects of alcohol content and see if high quality wines still
have more residual sugar. Since we also know that volatile acidity and chlorides
decrease the quality of alcohol, we can see what happens to residual sugar
when we adjust for those effects as well.

```{r echo=FALSE}
summary_type_median <- geom_line(aes(color = quality.type), stat = 'summary', 
                                 fun.y = median)

ggplot(aes(x = round(alcohol/0.25)*0.25, y = residual.sugar), data = df) +
  summary_type_median

ggplot(aes(x = round(volatile.acidity/0.05)*0.05, y = residual.sugar), 
       data = df) + 
  summary_type_median

ggplot(aes(x = round(chlorides/0.05)*0.05, y = residual.sugar), data = df) +
  summary_type_median

```

In bivariate analysis, we thought the quality peaked when residual sugar was
around 6 or 8.5. We see that peak of 8.5 on the left side of this plot, but
the quality is medium. After adjusting for alcohol content, High quality wines 
have the lowest amount of residual sugar compared to low and medium quality 
wines. Low quality wines tend to be high in residual sugar for the greatest
range of alcohol content values.

After adjusting for volatile acidity, there is no clear relationship. It looks
like high quality wines have more residual sugar than medium quality wines, but
is split 50-50 between low quality wines.

After adjusting for chloride content in a wine, high quality wines tend to have
more residual sugar compared to lower quality wines.

There was also a lot of correlation between fixed acidity, volatile acidity,
and citric acid. We can examine what happens to the quality of wine when
we adjust for each one the three acids and compare it to the other two acids.

```{r echo=FALSE}

ggplot(aes(x = round(fixed.acidity/0.25)*0.25, y = volatile.acidity), 
       data = df) +
  summary_type_median

ggplot(aes(x = round(fixed.acidity/0.25)*0.25, y = citric.acid), data = df) +
  summary_type_median

ggplot(aes(x = round(citric.acid/0.05)*0.05, y = volatile.acidity), 
       data = df) +
  summary_type_median

ggplot(aes(x = round(citric.acid/0.05)*0.05, y = fixed.acidity), 
       data = df) +
  summary_type_median

ggplot(aes(x = round(volatile.acidity/.05)*.05, y = fixed.acidity), 
       data = df) +
  summary_type_median

ggplot(aes(x = round(volatile.acidity/.05)*.05, y = citric.acid), 
       data = df) +
  summary_type_median

```

Adjusting for fixed acidity, higher quality wines tend to have lower volatile
acidity content and higher amount of citric compared to medium and low quality
wines. Very high citric acid or volatile acidity is only associated 
with low quality wines.

Adjusting for citric acid, higher quality wines tend to have lower volatile
acidity content compared to medium and low quality wines. Low quality wines
have the highest volatile acidity content.There is no clear relationship of
fixed acidity after adjusting for citric acid between the wine qualities. Low
qualities wines just tend to have higher fixed acidity than medium and high
quality wines.

Adjusting for volatile acidity, there is no clear relationship. It looks like
high quality wines have higher fixed acidity and citric acid content compared
to medium and low quality wines. This makes sense because higher fixed acidity
and citric acid content is associated with higher quality wines.

I hypothesize that the density of the wine and sugar might be related. We
previously found that higher wines tend to be a bit less dense but this could
be due to that they have less sugar.

```{r echo=FALSE}

ggplot(aes(x = round(residual.sugar/0.5)*0.5, y = density), data = df) +
  summary_type_median

```

After adjusting for residual sugar, high quality wines tend to be less dense
compared to medium quality wines but is split 50-50 between low quality wines.

We saw that higher pH was associated with higher wine quality, but this may be
due to that higher quality wines have higher acid content.

```{r echo=FALSE }

ggplot(aes(x = round(fixed.acidity/0.25)*0.25, y = pH), 
       data = df) +
  summary_type_median

ggplot(aes(x = round(volatile.acidity/0.05)*0.05, y = pH), 
       data = df) +
  summary_type_median

ggplot(aes(x = round(citric.acid/0.05)*0.05, y = pH), 
       data = df) +
  summary_type_median

```

After adjusting for acid content, it's apparent that pH does not affect wine
quality.

In bivariate analysis we didn't see a straight forward relationship between
chlorides and wine quality. We saw that chlorides have weak to weak-moderate
correlations with citric acid, alcohol, sulphates, density, and pH. We know
that pH and density doesn't affect wine quality, but citric acid, alcohol, and
sulphates do. 

We will check what happens with chlorides when we adjust for each
of these 3 variables.

```{r echo=FALSE}

ggplot(aes(x = round(citric.acid/0.05)*0.05, y = chlorides), 
       data = df) +
  summary_type_median +
  coord_cartesian(ylim = c(0, 0.15))

ggplot(aes(x = round(alcohol/0.25)*0.25, y = chlorides), 
       data = df) +
  summary_type_median +
  coord_cartesian(ylim = c(0, 0.15))

ggplot(aes(x = round(sulphates/0.05)*0.05, y = chlorides), 
       data = df) +
  summary_type_median +
  coord_cartesian(ylim = c(0, 0.20))

```

After adjusting for citric acid, we find that higher quality wines have
less chlorides. 

After adjusting for alcohol, there is no clear relationship

After adjusting for sulphates, we find that higher quality wine have less
chlorides.


# Multivariate Analysis

### Talk about some of the relationships you observed

High quality wine on average exhibit a total sulfur dioxide of between 15 to
50 depending on the ratio of free sulfur dioxide to total sulfur dioxide which
should be between 0.15 and 0.75.

After adjusting for alcohol content, higher quality wines tend to have a low
amount of residual sugar compared to lower quality wines. This is opposite of
what we found earlier that high quality wine are associated with high residual
sugar. After adjusting for chlorides, we did find that high quality wines
have more residual sugar content compared to the other wine.

Adjusting for each of the three acids, we find that high quality wine is indeed
associated with low volatile acidity, high fixed acidity, and high citric acid
content.

In bivariate analysis we saw a clear trend that high quality wine was less dense
compared to lower qualities. Here, we found that after adjusting for residual
sugar, it is less dense compared to medium quality wines but only less dense
half the time when compared to low quality wine. 

After adjusting for acid content, pH does not affect wine quality

After adjusting for citric acid and sulphates, we find that high quality
wine are associated with lower amounts of chloride.


### Were there any interesting or surprising interactions between features?
The most surprising was finding the opposite compared to the bivariate analysis.
For an example, we saw that more residual sugar on average meant higher wine
quality. Here, we see that high quality wine have low amounts of residual
sugar. There was also a surprise with the pH having nothing to do with wine
quality. We also found that the ratio of free sulfur dioxide to total sulfur
dioxide didn't increase quality of wine as it increases, but having a certain
total sulfur dioxide content paired with a certain ratio does increase wine
quality.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}

ggplot(aes(x = free.total.sulfur, y = round(total.sulfur.dioxide/10)*10), 
       data = df) +
  geom_point(aes(color = quality.type)) +
  geom_smooth(aes(color = quality.type), method = lm, level = 0.50) +
  coord_cartesian(ylim=c(0,80)) +
  scale_x_continuous(breaks = seq(0,1,0.10)) +
  scale_y_continuous(breaks = seq(0,300,10)) +
  labs(y = expression ('Total Sulfur Dioxide '~mg/dm^3),
       x = 'Ratio of Free Sulfur Dioxide to Total Sulfur Dioxide',
       color = 'Wine Quality',
       title = 'Free and Total Sulfur Dioxide Impact on Wine Quality')
  
```

### Description One
The plot shows the ideal total sulfur dioxide content in the wine based on
the ratio of free sulfur dioxide to total sulfur dioxide.

### Plot Two
```{r echo=FALSE, Plot_Two}
ggplot(aes(x = quality.type, y = alcohol), data = df) +
  geom_boxplot() +
  xlab('Wine Quality') +
  ylab('Alcohol Percentage') +
  ggtitle('Boxplot of Alcohol Content With Wine Quality') +
  scale_y_continuous(breaks = seq(0,20,0.5))

```

### Description Two
This plot clearly shows that the majority of high quality wine have higher
alcohol content compared to lower quality wine.

### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(aes(x = round(alcohol/0.25)*0.25, y = residual.sugar), data = df) +
  geom_line(aes(color = quality.type), stat = 'summary', fun.y = median) +
  labs(y = expression ('Residual Sugar '~g/dm^3),
       title = 'Residual Sugar versus Alcohol Percentage w/ Wine Qualities',
       x = 'Alcohol Percentage',
       color = 'Wine Quality') +
  scale_x_continuous(breaks = seq(5,15,1)) +
  scale_y_continuous(breaks = seq(0,10,0.5)) 
  
```

### Description Three
This plot shows that after adjusting for alcohol content, high quality wine have
low amounts of residual sugar compared to lower quality wine.

------

# Reflection

I started data exploration with univariate analysis on each chemical attribute
of red wine. The data was tidy and each column had the correct data type.I 
found the distribution of every variable and under quality, I noticed that it
could be separated into low, medium, and high quality wine based on the grouping 
of points.

With bivariate analysis, I found that higher quality wines are associated with
higher fixed acidity, lower volatile acidity, higher citric acid, lower density,
higher pH, higher sulphate, higher alcohol content, higher residual sugar,
less chlorides, and total sulfur dioxide content between 15 and 50 with
certain ratios of free sulfur dioxide to total sulfur dioxide from 0.15 to 0.75.

With multivariate analysis, some of the trends I found in bivariate were not
completely true. Higher quality wines tend to have low residual sugar after
taking into account the alcohol percentage of wines. After adjusting for acid
content, pH does not affect wine quality. 

Overall I noticed that the bivariate analysis is not completely reliable when
you don't adjust for certain variables. I did not look into every
multivariate plot possible to see if there were other variables found to
have a certain relationship under bivariate change under multivariate
conditions.

There are several limitations to this analysis. The first one is that the way
I defined the wine quality does not necessarily represent the high, medium, and
low wine qualities, so trends found only rely on the original definition. High
quality wine is rated 7 or 8. Medium quality is 5 or 6. Low quality is 3 or 4.
The second limitation is that the data contains only Portugeuse "Vinho Verde" 
red wines, so the conclusions and trends found here only apply to those group
of wines and not red wines in general. Another limitation could be the presence
of lurking variables. For an example, the age of the wine could impact wine
quality.There were also a lot of medium quality wine but not a lot of high
quality wine or low quality wine, so the observations for some of the plots
may have occurred due to chance.

For future work with this dataset, more multivariate analysis can be done.
Instead of looking at just the different quality of wine, you could separate
other variables into groups and compare it with quality and another variable.
More variables could be included such as ratios between variables and create
more complex visualizations that plot between two different ratios and find
the ideal ratio of certain attributes. It could be the case that some attributes
are not simple in that more is always better or less is always better. We saw
that with free sulfur dioxide. We also saw that the three acid attributes
were correlated with each other. Statistical models can also be created or
machine learning models to predict wine quality based on the chemical
attributes. Bootstrapping could be applied to the dataset to achieve higher
counts of low quality and high quality wine. This could potentially change
some of the trends found in this analysis.

